Pythran: Bringing OpenMP to a Python Subset

### 2013-01-27 doc/papers/europar2013/paper.tex
Take into account Pierrick's review.

In the manycore area, relying on parallelism to balance the performance
limitations of scripting languages, as described in~\cite{choy05} in the context
of the MATLAB language, or in~\cite{mals07} in the context of the R language.
In the context of Python, most approaches have focused on processes.

@@

An opposite approach consists in using the host language --- herein Python ---
to describe both parts of the system, and to let an automated tool perform the
translation to native code of a part of the application, generally the
computation-intensive one where parallelism has been expressed in some ways.
Thus, developers not familiar with lower level language or not eager to invest
the additional development time can still benefit from a fair performance boost.
This approach has been subject to many studies that can be classified based on
their backward-compatibity with the host language.

>>>>

In the many cores area, turning to parallelism to balance the performance
limitations of scripting languages, as described in~\cite{choy05} in the context
of the MATLAB language, or in~\cite{mals07} in the context of the R language,
seems legitimate. In the context of Python, most approaches have
focused on fork-based parallelism.

@@

An opposite approach consists in using the host language ---herein Python---
to describe both parts of the system, and to let an automated tool perform the
translation to native code of a part of the application, generally the
computation-intensive one where parallelism has been expressed in some ways.
Thus, developers not familiar with lower level language or not eager to invest
the additional development time can still benefit from a fair performance boost.
This approach has been subject to many studies that can be classified based on
their backward-compatibity with the host language.
